### 2017-04-05 doc/manuscript.Rmd
Edits to manuscript abstract as per Tony's edits

@@

Hypertriglyceridemia is an extensively studied and well described disorder in
the dysregulation of metabolic function and subsequent negative health outcomes [@Chehade2013a].
It is a strong risk factor for cardiovascular disease [@DAgostino2004a], in addition to other metabolic disorders such as non-is involved in metabolic dysfunction [@Verges2015a; @Kawano2013a; @Alberti2009a]. 
Circulating triacylglceride (TAG) concentration is commonly measured during
routine clinical assessment using enzymatic methods.
However, clinically measured TAG is limited as it
represents the full fatty acid spectrum within the TAG fraction as a summary
measure. There is increasing appreciation for the importance of specific fatty 
acid composition profiles in different plasma fractions on various health
outcomes [@Forouhi2014a; @Ma2015a; @Johnston2016a], however there are relatively
few studies that have explored the impact of the fatty acid composition in the TAG fraction [@Rhee2011a; @Lankinen2015a].

>>>>

Word count: 234 / 250

**Objective**: 
Although elevated serum triglyceride (TAG) is a well-described risk factor for
type 2 diabetes, few data are available regarding the role of the specific fatty
acid composition within serum TAG (TAGFA). In this context, our aim was to
examine longitudinal associations of TAGFA with insulin sensitivity (IS) and
beta-cell function.

**Research Design and Methods**:
We used longitudinal data (3 visits over 6 years) from the Prospective
Metabolism and Islet Cell Evaluation (PROMISE) cohort of adults (n=477) at-risk
for diabetes. Glucose and insulin from an OGTT were used to calculate the
Matsuda index (ISI), HOMA2-%S, the Insulinogenic Index over HOMA-IR (IGI/IR),
and the Insulin Secretion-Sensitivity Index-2 (ISSI-2). Gas chromatography
quantified TAGFA composition. Generalized estimating equations (GEE) adjusted for
confounders and partial least squares (PLS) were used for the analysis.

**Results**: 
The outcome variables declined by 14% to 27% over the 6-years. In the adjusted
GEE models with TAGFA as mol%, four TAGFA (14:0, 16:0, 14:1n-7, 16:1n-7) had
strong negative associations while most others (e.g. 18:1n-7, 18:1n-9, 20:2n-6, 
20:5n-3) had strong positive associations. Few associations were seen for 
beta-cell function, except for 16:0 (negative) and 18:1n-7 (positive). PLS
analysis indicated that four TGFA clustered together and strongly predicted
lower IS. These four TAGFA also correlated highly (r>0.4) with clinically
measured TAG.

**Conclusions**:
We found that higher proportions of a cluster of four TAGFA (14:0, 14:1-7,
16:0, 16:1n-7) strongly predicted lower IS as well as hypertriglyceridemia.

@@

Hypertriglyceridemia is an extensively studied and well described disorder in
the dysregulation of metabolic function and subsequent negative health outcomes [@Chehade2013a].
It is a strong risk factor for cardiovascular disease [@DAgostino2004a], in addition to other metabolic disorders such as non-is involved in metabolic dysfunction [@Verges2015a; @Kawano2013a; @Alberti2009]. 
Circulating triacylglceride (TAG) concentration is commonly measured during
routine clinical assessment using enzymatic methods.
However, clinically measured TAG is limited as it
represents the full fatty acid spectrum within the TAG fraction as a summary
measure. There is increasing appreciation for the importance of specific fatty 
acid composition profiles in different plasma fractions on various health
outcomes [@Forouhi2014a; @Ma2015a; @Johnston2016a], however there are relatively
few studies that have explored the impact of the fatty acid composition in the TAG fraction [@Rhee2011a; @Lankinen2015a].
